% Resume (and underlying template) (C) Avi Glozman, 2019-2024.
% See LICENSE for more information.

\documentclass[10pt]{article}
\usepackage[a4paper,  margin=0.25in, top=0.3in, bottom=0.3in]{geometry}
\usepackage{hyperref}

\usepackage[dvipsnames]{xcolor}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif

\usepackage[many]{tcolorbox}
\usetikzlibrary{decorations.pathreplacing}

% Source: https://tex.stackexchange.com/a/277825
% I also include some personal customization.
\newtcolorbox{leftli}{
    enhanced jigsaw, 
    breakable, % allow page breaks
    frame hidden, % hide the default frame
	colback=gray!15,
    overlay={%
        \draw [
            fill=none, % fill paper
			decoration={brace,amplitude=0},
            decorate,
            thin,
            black
        ]
        % right line
        (frame.south west)--(frame.north west);
    },
    % paragraph skips obeyed within tcolorbox
    parbox=false,
}

\begin{document}
	\pagestyle{empty}
	\begin{center}
		{\huge \textbf{Avi Glozman}} {\large \hfill 425.802.6718 -- \href{mailto:avi@avigloz.net}{avi@avigloz.net} -- NYC} \\
		%\vspace{0.5mm}
		{\large \textsl{Backend Software Engineer} \hfill \href{https://avigloz.net}{avigloz.net} -- \href{https://github.com/avigloz}{github.com\texttt{/}avigloz}}
	\end{center}
	
	\begin{flushleft}	
		\vspace{-0.5mm}
		{\large \raggedright \textbf{Skills}}
		\vspace{1.25mm}
	
		\hrule
	
		\vspace{2.25mm}
		\textbf{Programming Languages:} Haskell, Python, JavaScript (Node.js, Typescript), C\verb!#!, HTML\texttt{/}CSS\\
		\vspace{0.5mm}
		\textbf{Concepts:} REST APIs, Distributed Systems, System Design\texttt{/}Architecture, MFA\\
		\vspace{0.5mm}
		\textbf{Software:} SQL (PostgreSQL), NoSQL (MongoDB, DynamoDB), Object storage (S3), Git, Linux, AWS, \LaTeX\\ 
		\vspace{0.5mm}
		\textbf{Spoken Languages:} English (Native), Russian (Native), Spanish (Rusty Intermediate), Hebrew (Elementary)

		\vspace{1.5mm}
		{\large \raggedright \textbf{Experience}}
		\vspace{1.25mm}
	
		\hrule

		\vspace{2.25mm}

		\textbf{Mercury}, {\small hybrid from New York, NY}\\
		\begin{leftli}
			{\small \textbf{Backend Software Engineer II, \href{https://mercury.com/credit}{Cards}} \hfill \textit{\small Aug. 2023 $\rightarrow$ Now}}\\
			{\small \textbf{Backend Software Engineer, Cards}\hfill \textit{\small Jun. 2022 $\rightarrow$ Aug. 2023}}\\
			{\footnotesize \textit{Fun fact: I learned Haskell on the job from scratch!}}
			\begin{itemize}
				\item Writing robust, purely-functional, and test-driven Haskell to support Mercury's IO card and credit platform
				\vspace{-2mm}
				\item Building APIs and automation in administrative dashboards for managing customer credit lines
				\vspace{-2mm}
				\item Developing efficient and seamless collection tools for mitigating credit risk and enabling new credit products
				\vspace{-2mm}
				\item Owning projects end to end, from research and specification, to implementation and support
			\end{itemize}
		\end{leftli}

		\vspace{-1.50mm}
		\textbf{Stream}, {\small remote from New York, NY}\\
		\begin{leftli}
			{\small \textbf{Backend Software Engineer and Architect, \href{https://www.streamorders.com/product-features/full-control}{SmartMenu}} \hfill \textit{\small Apr. 2021 $\rightarrow$ Jun. 2022}}\\
			\begin{itemize}
				\item Led design and development of SmartMenu, a first-of-its-kind system that allows for same-day restaurant onboarding
				\vspace{-2mm}
				\item Integrated Stripe payments to enable users to subscribe to Stream, and built related API and backend framework
				\vspace{-2mm}
				\item Deployed data streaming architecture on AWS for analytics and big data with S3, Elasticsearch, and Kinesis
				\vspace{-2mm}
				\item Wrote test-driven, fast and elegant Node.js code in an Agile manner and reported directly to the CTO
			\end{itemize}
		\end{leftli}

		\vspace{-1.50mm}
		\textbf{Uber}, {\small Pittsburgh, PA}\\
		\begin{leftli}
			{\small \textbf{Software Engineering Intern, \href{https://www.uber.com/us/en/atg/research-and-development/perception-and-prediction/}{Advanced Technologies Group (ATG)}, Simulation}} \hfill \textit{\small May 2019 $\rightarrow$ Aug. 2019 (freshman summer)}\\
			{\footnotesize \textit{Fun fact: ATG was acquired by Aurora in Dec. 2020!}}
			\begin{itemize}
				\item Created an ETL system using Python for moving self-driving car related data from DynamoDB to PostgreSQL, and solved complex data-syncing challenges
				\vspace{-2mm}
				\item Developed pruning algorithms in Python for preventing transfer of broken, invalid, and\texttt{/}or redundant data relating to self-driving car testing
				\vspace{-2mm}
				\item Contributed significantly to a web API written in Go for self-driving car data analysis in production
			\end{itemize}
		\end{leftli}

		\vspace{-1.50mm}
		\textbf{Aspace}, {\small Seattle, WA}\\
		\begin{leftli}
			{\small \textbf{Lead Software Engineer, Backend}} \hfill \textit{\small May 2017 $\rightarrow$ Oct. 2017 (11\textsuperscript{th}\texttt{-} 12\textsuperscript{th} grade)}

			\begin{itemize}
				\item Deployed MySQL and MongoDB databases for storing parking spot sensor data and user data, respectively
				\vspace{-2mm}
				\item Designed a RESTful API written in Node.js to support UX on Android and iOS apps, and for recieving sensor data
				\vspace{-2mm}
				\item Wrote an implementation of Dijkstra's algorithm using Node.js for navigation, relying on user location data and data from Mapbox's API
				\vspace{-2mm}
				\item Used Twilio's SMS API to integrate two-factor authentication into the backend
			\end{itemize}
		\end{leftli}

		\vspace{1.5mm}
		{\large \raggedright \textbf{Education}}
		\vspace{1.25mm}
	
		\hrule
		
		\vspace{2.25mm}
		\textbf{University of Pittsburgh}, Pittsburgh, PA\\
      	{\small B.Sc. in Computer Science, \textbf{3.4 in-major, 3.2 overall} \hfill \textit{Aug. 2018 $\rightarrow$ Dec. 2020}}\\
		{\small \textbf{Dean's List:} \textit{Spring 2020, Fall 2020}}\\

		\vspace{1.25mm}
		{\large \raggedright \textbf{Interests}}
		\vspace{1.25mm}
	
		\hrule
	
		\vspace{2.25mm}
		Private Online CS Tutor \hfill \textit{\small Oct. 2017 $\rightarrow$ Now}\\
		Wikipedia Contributor (under username \textit{Avigl}) --- \href{https://pageviews.wmcloud.org/?project=en.wikipedia.org&platform=all-access&agent=user&redirects=0&range=all-time&pages=Timeline_of_social_media|Timeline_of_online_advertising|Timeline_of_e-commerce|Screening_Partnership_Program|Silicon_Valley_Education_Foundation|Chicago_Community_Trust}{over 1.2M all-time aggregate views} \hfill \textit{\small June 2016 $\rightarrow$ Now}\\
		Functional programming, neuroscience\texttt{/}biology, finance, music, metaphysics\texttt{/}ontology, writing poetry, history, videogames

		\vspace*{\fill}
		\textbf{\small Currently omitted or in-progress sections:}\\ 
		\textit{\small Personal projects, Publications, certain Skills (ones I haven't used in a while)}\\
		{\footnotesize \textit{For my personal projects, check out my GitHub!}}
	\end{flushleft}
\end{document}
